Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-04-23 sections/1stratified.tex
until 2.3

\begin{construction}\label{con:d_1^bor_structure}
    Consider the $\infty$-subcategory $\mathsf{D}_1^{\partial} \subset \bsc$ whose objects are $\mathbb{R}$ and $\hoint = \cone(\ast)$. There is a unique right fibration $\mathsf{D}_1^{\partial, \mathsf{or}} \rightarrow \mathsf{D}_1^{\partial}$, whose fiber over $\mathbb{R}$ is a point $\{ \mathbb{R}\}$, and whose fiber over $\hoint$ is two points $\{ \hoint, {\mathbb{R}_{\leq 0}} \}$. In other words, $\mathsf{D}_1^{\partial, \mathsf{or}}$ has objects $\mathbb{R}$, $\hoint$ and $\mathbb{R}_{\leq 0}$ with their canonical orientations, and the morphisms are orientation preserving embeddings between them. In this way, $\mathsf{D}_1^{\partial, \mathsf{or}}$ is the $\infty$-category of basics that describes oriented (or, equivalently in this case, framed), smooth 1-manifolds with boundary.
\end{construction}

\begin{remark}
    Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence. For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ controls framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms. On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[\href{https://kerodon.net/tag/018Y}{018Y}]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[\href{https://kerodon.net/tag/018F}{018F}]{lurie_kerodon}, \cite{joyal}). Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full $\infty$-subcategory is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well. In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism. However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Spaces}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures. By unstraightening, this determines a right fibration for which, by abuse, we write $\mathsf{D}^G_n=\mathsf{B}G\to \mathsf{D}_n\hookrightarrow\bsc$.
\end{remark}

>>>>

\begin{construction}\label{con:d_1^bor_structure}
    Consider the $\infty$-subcategory $\mathsf{D}_1^{\partial} \subset \bsc$ whose objects are $\mathbb{R}$ and $\hoint = \cone(\ast)$. There is a unique right fibration $\mathsf{D}_1^{\partial, \mathsf{or}} \rightarrow \mathsf{D}_1^{\partial}$, whose fiber over $\mathbb{R}$ is a point $\{ \mathbb{R}\}$, and whose fiber over $\hoint$ is two points $\{ \hoint, {\mathbb{R}_{\leq 0}} \}$. In other words, $\mathsf{D}_1^{\partial, \mathsf{or}}$ has objects $\mathbb{R}$, $\hoint$ and $\mathbb{R}_{\leq 0}$ with their canonical orientations, and the morphisms are orientation preserving embeddings between them. In this way, $\mathsf{D}_1^{\partial, \mathsf{or}}$ is the $\infty$-category of basics that describes oriented (or, equivalently in this dimension, framed), smooth 1-manifolds with boundary.
\end{construction}

\begin{remark}\label{16GY5V1}
    Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence. For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ controls framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms. On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[\href{https://kerodon.net/tag/018Y}{018Y}]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[\href{https://kerodon.net/tag/018F}{018F}]{lurie_kerodon}, \cite{joyal}). Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full $\infty$-subcategory is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well. In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism. However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Spaces}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures. By unstraightening, this determines a right fibration for which, by abuse, we write $\mathsf{D}^G_n=\mathsf{B}G\to \mathsf{D}_n\hookrightarrow\bsc$.
\end{remark}
